% $  Id: conclusion.tex  $
% !TEX root = main.tex

\begin{abstract}
With the popularization of deep-learning by google, artificial intelligence and machine learning have become the most sought after topics in computer science. However, there is little understanding about the internals of this domain, leading to the incorrect application of artificial intelligence techniques in distinct software projects. This paper provides an overview of artificial intelligence and machine learning, presenting the principal characteristics of existing techniques. Additionally, the paper provides a perspective about the applicability and usability of such techniques in diverse software projects.
Machine Learning has become a topic of interest because of its large field of application (deepen). Artificial intelligence is a broad area of knowledge comprised with several branches where each one has a different configuration and purpose. As a result, we consider one question: what field should a new user start working with if the goal is to classify information from a specific data set? Our work responds to this question based on empirical experimentation where we identified that approaching Machine Learning through supervised linear regression models allows users to understand the basic applications while fulfilling their objective. Moreover, due to available resources such as high level TensorFlow Estimator API and the column-oriented data analysis API Pandas learning doesn’t require long(subjective) before the user can start working on Machine Learning proyects. 

With the popularization of Deep-Learning by Google, Artificial Intelligence and Machine Learning have become the most sought after topics in Computer Science. However, there is little understanding about the internals of this domain, leading to the incorrect application of artificial intelligence techniques in distinct software projects. This paper provides an overview of Artificial Intelligence and Machine Learning, presenting the principal characteristics of existing techniques. Because of the variety of techniques and applications we consider one question: what field should a new user start working with if the goal is to classify information from a specific data set? Our work responds to this question based on empirical experimentation where we identified that approaching Machine Learning through supervised linear regression models allows users to understand the basic applications while fulfilling their objective. Moreover, this paper provides a perspective about the applicability and usability of such techniques.


\end{abstract}


\endinput


